---
title: "NIMBLE Project Report"
author: "Tristan Sones-Dykes"
date: "Date: `r format(Sys.Date(), '%B %d, %Y')`"
output:
  pdf_document:
---

```{r, echo=FALSE, results=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(here)
library(nimble)

df <- read_csv(here("input.csv"))
```

# Data

The input data format is as follows:

| yi  | xi  | zi  |
|---- |---- |---- |
| ... | ... | ... |

The variables represent the total length of time spent telephoning (yi), the number of telephone calls made (xi), and a binary feature for weekdays (zi).

# Model Specification

## Likelihood

The model assumes a linear relationship between the response variable (yi) and the explanatory variables (xi and zi) as follows:

\[ yi = \alpha + \beta xi + \gamma zi + \epsilon_i \]

Where \( \epsilon_i \sim N(0, \sigma^2) \) represents the error term.

## Priors

The prior distributions of the variables are as follows:

- \( \alpha \sim N(µ_{\alpha}, \sigma^2_{\alpha}) \)
- \( \beta \sim N(µ_{\beta}, \sigma^2_{\beta}) \)
- \( \gamma \sim N(µ_{\gamma}, \sigma^2_{\gamma}) \)
- \( \sigma^2 \sim \Gamma^{-1}(a, b) \)

(1)
Vague priors for these are:

- \( \alpha \sim N(0, 10^5) \)
- \( \beta \sim N(0, 10^5) \)
- \( \gamma \sim N(0, 10^5) \)
- \( \sigma^2 \sim \Gamma^{-1}(0.0001, 0.0001) \)

This ensures both the normals and inverse gamma is very flat, and therefore vague.

\newpage

# Data Analysis

## Exploration

(2a) The data is plotted below:

```{r}
ggplot(df, aes(x = xi, y = yi, colour = factor(zi))) + 
    geom_point() + 
    labs(x = "Number of calls", 
    y = "Time spent telephoning (mins)", 
    colour = "Weekday", 
    title = "Time spent telephoning vs. number of calls")
```

Looking at the plot, the model seems very reasonable. There is a clear linear relationship between
xi and yi, and the binary feature zi has very little mixing between the two classes.

\newpage

## Model Fitting

(2b) The model is fitted using the following code:

```{r}
